\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-10-19 latex/whitepaper/article.tex
update minor fix
minor fix
typo

\address[1]{\centering DAO Advisor, Syscoin Platform (e-mail: cyotee@syscoin.org)}
\address[2]{\centering  Syscoin Researcher, Syscoin Platform (e-mail: imoore@syscoin.org)}
\address[3]{\centering  L2 Advisor, Syscoin Platform (e-mail: rylandarbour@syscoin.com)}
\address[4]{\centering Syscoin Lead Developer, (e-mail: sidhujag@syscoin.org)}
\tfootnote{}

@@

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a five-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. Overall, we are predicting an overall return of 14.7M SYS which represents a five-year return of 36.8\% from the original investment of 40M SYS; see Fig. \ref{fig:reward_output}. Without DAOSYS, we would only realize an overall return of 31.2\%. Keep in mind that the principle investment of 100K SYS is not subject to risk as the estimated DAOSYS returns are utilizing Masternode returns as its principle. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the five-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/index_coin.png}
\caption{Comparison of various Bithereum index coin market weighting strategies beginning at the 2020 BTC halvening with \$1 initial investment. We see that compared to just BTC alone, that a 50/50 weighting of BTC and ETH would outperform BTC by approximately 16 times.} 
\label{fig:crypto_index}
\end{figure}

@@

\begin{equation}
\label{eqn:trend}
	\mathbf{\hat{p}}_{t} = c + \mathbf{\tilde{z}}_{t}e^{k z_{t}},
\end{equation}
where random drift term $\mathbf{\tilde{z}}_{t}$ is normalized between the interval [$a_{lwr}$,$a_{upr}$] as given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})},
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t},
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coefficient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. For a table of these point predictions along with its corresponding confidence interval, see \cite{Moo22A}.

>>>>

\address[1]{\centering DAO Advisor, Syscoin Platform (e-mail: cyotee@syscoin.org)}
\address[2]{\centering  Syscoin Researcher, Syscoin Platform (e-mail: imoore@syscoin.org)}
\address[3]{\centering  L2 Advisor, Syscoin Platform (e-mail: rylandarbour@syscoin.org)}
\address[4]{\centering Syscoin Lead Developer, (e-mail: sidhujag@syscoin.org)}
\tfootnote{}

@@

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a five-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the five-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.

Overall, we are predicting an overall return of 14.7M SYS which represents a five-year return of 36.8\% from the original investment of 40M SYS; see Fig. \ref{fig:reward_output}. Without DAOSYS, we would only realize an overall return of 31.2\%. Keep in mind that the principle investment of 100K SYS is not subject to risk as the estimated DAOSYS returns are utilizing Masternode returns as its principle.

@@

\begin{figure}[h!]
\includegraphics[width=3in]{img/index_coin.png}
\caption{Comparison of various Bithereum index coin market weighting strategies beginning at the 2020 BTC halvening with \$1 initial investment. We see that compared to just BTC alone, that a 50/50 weighting of BTC and ETH would outperform BTC by approximately 2x.} 
\label{fig:crypto_index}
\end{figure}

@@

\begin{equation}
\label{eqn:trend}
	\mathbf{\hat{p}}_{t} = c + \mathbf{\tilde{z}}_{t}e^{kt},
\end{equation}
where random drift term $\mathbf{\tilde{z}}_{t}$ is normalized between the interval [$a_{lwr}$,$a_{upr}$] as given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})},
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t},
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coefficient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. For a table of these point predictions along with its corresponding confidence interval, see \cite{Moo22A}.
